---
title: "Hw4"
author: "Arya Ranadive"
date: "6/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Indeed Data Frame


```{r dataframe, include=FALSE}
library("RCurl")
library("XML")
library("RJSONIO")

source("functions4hw4.r")
BaseURL = "https://www.indeed.com"
cookies = "CTK=1g55dnqbghsma801; ctkgen=1;JSESSIONID=EA2EC2FE26FDFEF7E0548929DE72B571; indeed_rcc=''; INDEED_CSRF_TOKEN=jjXg0roGHDo4cdOmQ9N2E5GFB7mWJ0nh; PREF='TM=1654818335100:L=California'; Version=1; Max-Age=157680000; UD='LA=1654818335:CV=1654818335:TS=1654818335:SG=4b34e9a7ef0be7004606e1d401c989b2'; Version=1; Max-Age=157680000;NBDVJ='';RQ='q=Data+Scientist&l=California&ts=1654818335125';jaSerpCount=1;"

con = getCurlHandle(followlocation = TRUE, cookie = cookies)
t = "https://www.indeed.com/jobs?q=Data%20Scientist&l=California&redirected=1&vjk=de2c067e43d5b964"


ds <- getIndeed(t, BaseURL, con, "Data Scientist")

```

```{r}
source("functions4hw4.r")
v = "https://www.indeed.com/jobs?q=Data%20Engineer&l=California&vjk=5d1f43db1475af44"
dr <- getIndeed(v, BaseURL, con, "Data Engineer")
```

```{r }
x = "https://www.indeed.com/jobs?q=Data%20Analyst&l=California&vjk=5d1f43db1475af44"
da <- getIndeed(x, BaseURL, con, "Data Analyst")
```

```{r}
da <- rbind(da, dr)
da <- rbind(da, ds)
head(da)
```

## Analysis

#### Comparing In-Person and Remote
Out of the 1800 jobs looked at, I looked at the total jobs that were remote, in-person, hybrid. I also looked at how many jobs were remote for the job categories that I looked at. 
```{r}
sum(da$Remote == 'Remote')
sum(da$Remote == 'In-Person')
sum(da$Remote == 'Hybrid')


sum(da$Remote == 'Remote' & da$JobCategory == 'Data Scientist')
sum(da$Remote == 'Remote' & da$JobCategory == 'Data Engineer')
sum(da$Remote == 'Remote' & da$JobCategory == 'Data Analyst')


```


#### Where are the jobs located? 
Here are the top 5 cities in California where the subset of jobs are located: 
```{r}
names(sort(table(da$Location), decreasing = TRUE)[1:6]) [-3]

```

#### Companies with the highest ratings?

```{r}

unique(subset(da, Ratings >= 5.0)$CompanyName)

```

## Largest Companies
Some of the largest companies (not listed in order) are listed below. 
```{r}

unique(subset(da, CompanySize = 'more than 10,000')$CompanyName)[1:10]

```

